Improving real-time trend estimates using local parametrisation of polynomial regression filters

### 2024-02-12 article_jos.qmd
remove local in title

---
title: "Improving real-time trend estimates using local parametrisation of local polynomial regression filters"
format:
  pdf:
    documentclass: article
    number-sections: true
    pdf-engine: pdflatex
    keep-tex: true
    toc: false
    include-in-header: [preamble.tex]
    #include-before-body: template/preambule.tex
    geometry:
      - top=2cm
      - bottom=2cm
      - left = 2.5cm
      - right = 2.5cm
    cite-method: biblatex
linestretch: 2
echo: false
tbl-cap-location: top
fig-cap-location: top
bibliography: biblio.bib
csl: chicago-author-date.csl
---

>>>>

---
title: "Improving real-time trend estimates using local parametrisation of polynomial regression filters"
format:
  pdf:
    documentclass: article
    number-sections: true
    pdf-engine: pdflatex
    keep-tex: true
    toc: false
    include-in-header: [preamble.tex]
    #include-before-body: template/preambule.tex
    geometry:
      - top=2cm
      - bottom=2cm
      - left = 2.5cm
      - right = 2.5cm
    cite-method: biblatex
linestretch: 2
echo: false
tbl-cap-location: top
fig-cap-location: top
bibliography: biblio.bib
csl: chicago-author-date.csl
---
